Manuscript figures

### 2021-07-16 docs/manuscript_figures.Rmd
Stage 1 :bookmark:

```{r}
library(sf)
library(raster)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(tidyr)
library(RStoolbox)

@@

# Figure
pts_nicfi_all <- merge(pts_nicfi_all, cols_lc[, 2:3])
ref_epl <- ggplot(pts_nicfi_all,
                  aes(x = Band, y = Reflectance / 1000,
                      color = ids)) +
    geom_point() + geom_line(show.legend = 'line') +
    ylab(bquote('Reflectance'~(10^3))) + 
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    scale_x_discrete(limit = 1:4,
                     labels = unique(pts_nicfi_all$`Band name`)) +
    theme_bw() +
    theme(axis.title.x = element_blank()) +
    facet_wrap(~ Season, nrow = 2, 
               scales = "free_y",
               strip.position = "right")

@@

# Make figure
pts_ts <- merge(pts_ts, cols_lc[, 2:3])
pts_fit <- merge(pts_fit, cols_lc[, 2:3])
ts_epl <- ggplot() + 
    geom_point(data = pts_ts, 
               aes(x = DOY, y = `dB`, 
                   color = factor(ids)),
               size = 0.6) +
    geom_line(data = pts_fit,
               aes(x = DOY, y = `dB`, 
                   color = factor(ids))) +
    facet_wrap(~polarization, 
               scales = 'free_y', nrow = 2,
               strip.position = "right") +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    theme_bw()

@@

# Read tiles
guess_tiles <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    pull(tile) %>% unique()
nicfi_tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson')) %>% 
    mutate(guess = ifelse(tile %in% guess_tiles, 1, 0))
samples <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    filter(score > 7)
sample_quality <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    filter(tile == '1228-999' & score > 7)

@@

>>>>

```{r}
library(sf)
library(raster)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(tidyr)
library(stringr)
library(RStoolbox)

@@

# Figure
pts_nicfi_all <- merge(pts_nicfi_all, cols_lc[, 2:3])
ref_epl <- ggplot(pts_nicfi_all,
                  aes(x = Band, y = Reflectance / 1000,
                      color = ids)) +
    geom_point() + geom_line(show.legend = 'line') +
    ylab(bquote('Reflectance'~(10^3))) + 
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    scale_x_discrete(limit = factor(1:4),
                     labels = unique(pts_nicfi_all$`Band name`)) +
    theme_bw() +
    theme(axis.title.x = element_blank()) +
    facet_wrap(~ Season, nrow = 2, 
               scales = "free_y",
               strip.position = "top")

@@

# Make figure
pts_ts <- merge(pts_ts, cols_lc[, 2:3])
pts_fit <- merge(pts_fit, cols_lc[, 2:3])
ts_epl <- ggplot() + 
    geom_point(data = pts_ts, 
               aes(x = DOY, y = `dB`, 
                   color = factor(ids)),
               size = 0.6) +
    geom_line(data = pts_fit,
               aes(x = DOY, y = `dB`, 
                   color = factor(ids))) +
    facet_wrap(~polarization, 
               scales = 'free_y', nrow = 2,
               strip.position = "top") +
    scale_color_manual("Land cover type",
                       values = cols_lc$cols, 
                       breaks = cols_lc$ids,
                       labels = cols_lc$`Land cover type`) +
    theme_bw()

@@

# Read tiles
guess_tiles <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    pull(tile) %>% unique()
nicfi_tiles <- read_sf(here('data/geoms/tiles_nicfi_north.geojson')) %>% 
    mutate(guess = ifelse(tile %in% guess_tiles, 1, 0))
samples <- read_sf(here('results/north/label_check_catalog.geojson')) %>% 
    filter(score > 7)

@@

## Metrics

```{r}
# Get file names
fns <- list.files(here('results/scalars/single_compose_lr'), 
                  pattern = 'compose_lr',
                  full.names = T)

# Metrics
fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
metrics_last10 <- do.call(cbind, lapply(fns, function(fn){
    read.csv(fn, stringsAsFactors = F) %>% 
        dplyr::select(-c(Wall.time, Step)) %>% 
        tail(10)
}))
names(metrics_last10) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

# Calculate mean and sd
items <- c('AA', 'IoU', 'Cropland', 'Forest', 
           'Grassland', 'Shrubland', 'Water', 
           'Urban', 'Bareland')
options(digits = 3)
tb <- do.call(rbind, lapply(items, function(item){
    vals <- metrics_last10 %>% pull(all_of(item))
    if (item == 'Urban') item <- 'Built-up'
    data.frame(mean = mean(vals),
               sd = sd(vals)) %>% 
        mutate(metric = item)
}))
```

## Scalars

```{r}
library(here)

# Single U-Net model with step learning rate
# Get file names
fns <- list.files(here('results/scalars/single_step_lr'), 
                  pattern = 'step_lr',
                  full.names = T)

# Learning rate
step_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
    mutate(Step = Step / 113)

# Scalars
fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
unet_step_lr_scalars <- lapply(fns, function(fn){
    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
        mutate(Step = Step / 113) %>% 
        dplyr::select(-Wall.time)
})
names(unet_step_lr_scalars) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

# Single U-Net model with compose learning rate
# Get file names
fns <- list.files(here('results/scalars/single_compose_lr'), 
                  pattern = 'compose_lr',
                  full.names = T)

# Learning rate
compose_lr <- read.csv(fns[2], stringsAsFactors = F) %>% 
    mutate(Step = Step / 113)

# Scalars
fns <- fns[str_detect(fns, 'Validate') & (!str_detect(fns, 'loss'))]
unet_compose_lr_scalars <- lapply(fns, function(fn){
    scalar <- read.csv(fn, stringsAsFactors = F) %>% 
        mutate(Step = Step / 113) %>% 
        dplyr::select(-Wall.time)
})
names(unet_compose_lr_scalars) <- gsub(
    '.csv', "", 
    str_extract(fns, '[A-Z]{1}[A-Z|a-z]+.csv'))

# Plot
aa <- merge(unet_compose_lr_scalars$AA, 
            unet_step_lr_scalars$AA, 
            by = 'Step') %>% 
    rename(Compose = Value.x, Cot = Value.y) %>% 
    pivot_longer(cols = c(Compose, Cot),
                 names_to = 'type', values_to = 'value')
ggplot(aa, aes(x = Step, y = value)) +
    geom_line(aes(color = type, lty = type)) +
    geom_smooth(aes(color = type)) +
    theme_bw()
```
